\section{APPENDIX}
\subsection{COMPETITION CLASSES}
Competitive classes are divided into two categories, defined by the
type of equipment allowed:

\textbf{Unequipped} - Only pen, paper, timepiece(s) and stock odometer permitted. No calculation equipment allowed (including average mph display). Three classes compete in this category:
\begin{itemize}
\item \textbf{Novice}- This class is intended for beginners only.
\item \textbf{SOP (Seat of Pants)} -This class is intended for intermediate level competitors.
\item \textbf{Masters} - This class is intended for experienced competitors.
\end{itemize}

\textbf{Equipped} - Navigational and calculation equipment is permitted as described below in the two classes that compete in this category:
\begin{itemize}
\item \textbf{Limited} - Navigational and calculation equipment is permitted in this class provided that such equipment does not receive a direct input from any distance-measuring device interfaced with the
vehicle. All inputs for mileage must be made manually. Calculators, personal computers, external odometers, average MPH display, and GPS units are permitted in this class.

\item \textbf{Unlimited} - As its name implies, this class is not limited in any way. Any contestant may compete in this class, regardless of equipment in use.
\end{itemize}

\subsection{FRIDAY NIGHTER RALLY SERIES CHAMPIONS}

%TODO bold font
%TODO table overflows page width
%TODO newline for 2010 tie (unequip nav)
\begin{tabular}{ |c|c|c|c|c| }
  \hline
  \multicolumn{1}{|c|}{} &
  \multicolumn{2}{|c|}{Unequipped} &
  \multicolumn{2}{|c|}{Equipped} \\
  \hline
  2012 & Larry Anson & Fran Hanchek & Brandon Harer & Chris Hale \\
  2011 & Brandon Harer & Marcus Gattman & April Song & Marcus Song \\
  2010 & Larry LeFebvre & \textit{tie}: Rick Vonk / \linebreak Jill Zurschmeide & Kevin Poirier & Chris Hale \\
  2009 & Steven Smith & John Masterman & April Smith & Marcus Song \\
  2008 & Jeff Zurschmeide & Jill Zurschmeide & April Smith & Marcus Song \\
  2007 & Matt Tabor & Marcus Gattman & April Smith & Marcus Song \\
  2006 & Jeff Zurschmeide & Jill Zurschmeide & Monte Saager & Victoria Saager \\
  2005 & Jeff Zurschmeide & Jill Zurschmeide & Brandon Harer & Marcus Song \\
  2004 & Jill Zurschmeide & Jeff Zurschmeide & April Smith & Ben Bradley \\
  2003 & Matt Tabor & Marcus Gattman & Monte Saager & Victoria Saager \\
  2002 & Jon Tabor & Darlene Tabor & Monte Saager & Victoria Saager \\
  2001 & Brandon Harer & Jennifer McGrew & Russ Kraushaar & Katy Wood \\
  \hline
\end{tabular}