\section{Main Road Determinants (MRDs)}
\label{sec:mrd} A main road exists at every intersection and is identified by applying the MRDs below.  For an MRD to apply, it must identify a single road leaving the intersection other than the one upon which the intersection was approached.  To determine that single road leaving the intersection, apply the MRDs in the order listed below.  If attempting to apply an MRD results in no choice or more than one choice, go on to the next MRD.

\subsection{ONTO}
The main road is the road that the execution of a route instruction has directed the contestant to travel upon by use of: (1) the terms ONTO or FOLLOW and (2) the designation (name, number, or letter(s)) of the road as identified by a sign.  The designated road is the main road at each intersection where this MRD applies until a deviation not labeled MBCU (requiring the contestant to leave the main road) is executed.

\subsection{TOWARD}
The main road is the road that the execution of a route instruction has directed the contestant to travel in the direction of a landmark by use of (1) the term TOWARD and (2) the designation (name, number, or letter(s)) of the landmark.  Follow signs in the direction of the landmark at each intersection where this MRD applies until a deviation not labeled MBCU (requiring the contestant to leave the main road) is executed.

\subsection{PROTECTION}
The main road is the single road which leaves the intersection without a back-facing stop or yield sign on it at the intersection.

\subsection{SURFACE}
The main road is the obvious continuation beyond an intersection of the road with the same type of surface as that which you approached the intersection on.  Only a paved versus unpaved distinction will be made.

\subsection{STRAIGHT AS POSSIBLE}
The main road is that single road which continues through the intersection in the straightest route.  If the routes appear to be equally straight, or no route requires less than a 45 degree course change, this MRD does not apply.

\subsection{LEFTMOST}
The main road is the leftmost road leaving the intersection.