\subsection{Championship Points Policy}
\subsubsection{Friday Nighter Series Trophies}
Season trophies are awarded to the drivers and navigators who accumulate the most points during the Friday Nighter Series, as follows:
\begin{itemize}
\item \textbf{Unequipped}: First, Second, Third, Fourth, Fifth, and Sixth Place
\item \textbf{Equipped}: First, Second, and Third Place
\end{itemize}

Points are awarded at each Friday Nighter based on a competitor’s overall placement within their category of competition (unequipped or equipped).
Unequipped includes SOP and Masters only – Novice entries do not count toward season points\footnote{
Novice competitors may be provided with special route instructions that provide significant course-following tips and rule explanations. Thus, it is recommended that teams remain in Novice class only until they have a good working knowledge of the rules. It is to their advantage to move up to the SOP class so they can earn Series Points. Three podium finishes in the Novice class indicates a good working knowledge of the rules.
}.
Unequipped competitors earn 25 points for finishing first, 24 for second, 23 for third, etc. Equipped competitors earn points similarly, but first place receives 10 points, 9 for second, 8 for third, and so on.
If there is a tie, both cars earn the same points for that position and the next position is skipped.
Drivers and navigators accumulate points separately.
All Friday Nighters are championship events.
Competitor’s best six of eight events count toward season total.
If there is a tie for season total points, the tie is resolved as follows:

\begin{enumerate}[i]
\item Fewest events run in the season
\item Most 1st place finishes, 2nd place, 3rd etc.
\end{enumerate}

\subsubsection{CSCC Championship Trophies}
Season trophies are awarded to the drivers and navigators who meet the eligibility requirements described below. Award is based on the points standings described above, as follows:
\begin{itemize}
\item \textbf{Unequipped}: First Place
\item \textbf{Equipped}: First Place
\end{itemize}

To be eligible, the competitor must be a Cascade member at the time of the event for which championship points are earned. In addition, the competitor must accumulate at least 10 CSCC worker points (20 volunteer hours) or served as a rallymaster during the season. Contact the Geargrinders Chair or CSCC Pointskeeper for more information about worker points.

\subsubsection{Event Tie Breaker Priority}
In case of a tie, for the purpose of awarding event trophies, the tie is resolved as follows:
\begin{itemize}
\item \textbf{a)} Most zeros
\item \textbf{b)} Most ones
\item \textbf{c)} Sum of squares
\end{itemize}
