\section{Procedures}

\subsection{Registration and Starting}
Locate the registrar. Get a registration packet and complete the registration process.

\begin{itemize}

\item The driver must have a valid driver's license and carry minimum insurance coverage(s) as required in the state where the vehicle is registered.

\item The driver must read and complete the vehicle self-inspection portion of the registration form in its entirety and sign where indicated.

\item Return the completed form and entry fee to the registrar. The registrar or Geargrinders Chair may ask for current evidence of CSCC membership to grant member pricing.

\item All participants (drivers, navigators, and passengers) must sign the ICSCC Insurance Liability Waiver form available at registration. Participants under the age of 18 must present a parent or legal guardian to the Geargrinders Chair who will witness the signing of the minor release form.

\item Failure to follow these mandatory registration guidelines can severely compromise our sport. This may lead to disqualification and/or exclusion from any and all Cascade Sports Car Club events.

\end{itemize}

The registrar will give you a car number, a score card, and route instructions.

Note the appearance of the official checkpoint, route control, or course marker signs displayed near the registrar.

Set your timepiece(s) to official time at the official time station located near the registrar. Start times are in one-minute increments based on car number.

Attend the informational meeting approximately fifteen minutes before the first car is due out.

No later than your assigned start time, leave the out marker at the starting point by following the route instructions.

\subsection{Odometer Calibration}
Each event includes after its start a clearly defined odometer calibration zone for the purpose of allowing each contestant's odometer to be compared to the official odometer. The odometer calibration zone is at least ten (10) miles long and contains intermediate mileage reference points. The odometer calibration zone is free of checkpoints and route controls.

\subsection{Checkpoints}
Stop at each checkpoint you encounter, as identified by an official checkpoint sign at the right side of the road on which you are traveling.

\begin{itemize}

\item Pull up to the control station beyond the checkpoint sign. Do not get out of line and do not leave your vehicle unless requested to do so by a rally official.

\item Give your scorecard and time declarations, if any, to the control station.

\item The control station will return your scorecard and time declarations, if any, indicating your End leg time (in time) and Start leg time (out time). You may receive supplemental instructions.

\item After receiving all information, proceed out to the out marker and time yourself out by your own timepiece.

\end{itemize}

\subsection{Route Controls}
Stop at each route control you encounter, as identified by an official route control sign on the right side of the road on which you are traveling.

\begin{itemize}

\item Pull up to the control station beyond the route control sign. Do not get out of line and do not leave your vehicle unless requested to do so by a rally official.

\item Give your scorecard to the control station.

\item The control station will return your scorecard. You will receive a PAUSE for the time spent stopping at the control and you may receive supplemental instructions which must be executed prior to resuming the numbered route instructions.

\end{itemize}

\subsection{Blocking a Control}
Safety at rally control locations is of utmost importance. When identifying and approaching a control, you may not block the entrance of the control by stopping in the roadway, unless you are legally obligated to do so. If a contestant is observed stopping in front of the control they are entering, they will be assessed a maximum leg score (300) and must immediately proceed to the control station.

\subsection{Drive Safely}
Contestants must obey all traffic laws and drive in a safe manner throughout the event. Contestants observed driving recklessly or in a manner which may imperil the safety of occupants of their own vehicle, other participants, or the public will be subject to disqualification from the event in progress and may be refused entry to subsequent event(s). Any contestant cited by a recognized law enforcement agency for a moving violation during the event will be automatically disqualified.

\subsection{Time Declarations}
To avoid speeding to make up lost time, contestants may make a declaration of time loss. A time declaration must be requested on the half-minute and cannot be claimed in even minutes (e.g., 0.50, 1.50, 2.50, etc.). Only one time declaration may be claimed for each leg. The time declaration must be submitted in writing at the next manned checkpoint prior to receipt of perfect leg time. Combined time declarations may not exceed a total of 19.50 minutes per event. The Geargrinders Chair has final authority on acceptance of submitted time declarations.

\subsection{Scorecard}
At the finish, turn in your completed scorecard. The Geargrinders Chair has final Authority on all decisions affecting how the event is scored. If the Geargrinders Chair is a competitor, then the Rallymaster Liaison shall arbitrate scoring decisions.