\section{Rally Route}

\subsection{Rally Route}
To follow the intended rally route, proceed by taking the following actions in the order listed:

\begin{itemize}

\item Execute emergency directions provided by a rally official.

\item Execute a supplemental route instruction provided at a control.

\item Execute a note route instruction.

\item Execute a numbered route instruction.

\item Follow the main road.

\end{itemize}

\subsection{Rally Roads}
A rally road is a public through road.  Unless otherwise directed, a rally road may be paved or unpaved.  Unless specifically described in the route instruction (i.e., you may use this dead end road), do not consider the following as valid rally roads.

\begin{itemize}

\item Roads marked ``PRIVATE'', ``KEEP OUT'', ``NO OUTLET'', ``DEAD END'', ``ROAD CLOSED'', ``NO THROUGH TRAFFIC'', etc.

\item Roads that are visibly barricaded or impassable.

\item Cul-de-sacs that visibly dead-end.

\item Roads that visibly dead-end.

\item Roads having illegal entry.

\item Roads requiring an illegal turn to enter.

\end{itemize}

\subsection{Intersections}
An intersection is any joining of rally roads from which the contestant could legally proceed in more than one direction without U-Turning.

A roundabout is a joining of rally roads where traffic travels counterclockwise around a central island.  Traffic enters the roundabout without deviation.  Once in the roundabout, the main road continues around the roundabout by PROTECTION since all deviations from the circular route are protected by yield signs.  If placed ONTO a road by name or number or TOWARD a landmark, the main road is the road exiting the roundabout as so identified by a sign.  Exiting a roundabout on the same road where the roundabout was entered is a legal deviation and is not considered a u-turn.

\subsection{U-turns}
No uninstructed U-turn(s) will be necessary to follow the rally route.

\subsection{Course Markers}
The club initials ``CSCC'' identify all course markers.

\begin{itemize}

\item On-course markers are bright green.

\item Off-course markers are bright orange.

\item Course correction markers are on-course markers upon which a route instruction number is written; execute that numbered route instruction at that location and continue in numerical order from that point on.

\item Roads posted with an off-course marker upon which ``DNE'' is written; do not consider such a road as a valid rally road.

\end{itemize}
