\documentclass[letterpaper,10pt]{article}
\setlength{\textheight}{419pt}   \setlength{\textwidth}{289pt}
\setlength{\oddsidemargin}{72pt} \setlength{\evensidemargin}{108pt}
\setlength{\topmargin}{55.9pt}   \setlength{\footskip}{27.5pt}
\setlength{\headheight}{14.6pt}  \setlength{\headsep}{19.9pt}

\setlength{\parindent}{0pt}
\setlength{\parskip}{1ex plus 0.5ex minus 0.2ex}

\usepackage[noprint,1to1]{booklet}
\usepackage{ifpdf}
\ifpdf
  \setpdftargetpages
\else
  \setdvipstargetpages
\fi
\ifprintoption
  \special{!TeXDict begin /landplus90{true}store end}
  \special{!TeXDict begin <</Tumble true>> setpagedevice end}
\fi

\newcommand{\hiddensubsection}[1]{
  \stepcounter{subsection}
  \subsection*{\arabic{section}.\arabic{subsection}\hspace{1em}{#1}}
}

\begin{document}

\pagestyle{empty}
\begin{titlepage}
Front cover stuff goes here.

[CSCC LOGO]

Road Rally Rules 2013
\end{titlepage}
\newpage

Welcome to the Cascade Sports Car Club's Road Rally Program. If you are new to
the sport or the area, feel free to contact a Geargrinders road rally official
for information or advice.

CSCC's time-speed-distance road rallies are conducted in accordance with these
Road Rally Rules. These rules may be modified by supplemental rules specific to
the event.

The object of a time-speed-distance road rally is to complete the rally route
\textbf{on course} and as close to \textbf{on time} as possible. Being \textbf{on
course} refers to arriving at official checkpoints having followed the route
intended by the rallymaster. Being \textbf{on time} refers to arriving at official
checkpoints having taken the amount of time intended by the rallymaster.

\textbf{Official time} -- indended or allowed time -- is the amount of
time it takes to drive the intended route at the average speeds specified in the
route instructions. The rally route is measured in thousandths of a mile from
speed change to speed change. Allowed time is computed to the nearest hundredth
of a minute.

Each hundredth of a minute that you arrive early or late on each leg is worth
one \textbf{penalty point}. A perfect leg score is \textbf{zero}, arriving exactly
on time. The maximum number of penalty points for any one leg is 300. If you are
three or more minutes early or late on any leg, your score for that leg is 300.

\begin{center}
\line(1,0){250}
\end{center}

To learn more about Cascade Sports Car Club's activities, visit www.cascadesportscarclub.org or write to: CSCC, P.O. Box 4304, Portland, OR 97208.

You are welcome to attend general club meetings on the first Saturday of each month, 8 p.m. (7 p.m. during winter), Stark Street Pizza, SE 92nd and Stark, Portland, Oregon.

For up-to-date information about CSCC Road rallies:
\begin{itemize}
  \item Call: 541-331-8651
  \item E-mail: rally@cascadesportscarclub.org
  \item Visit: www.cascadesportscarclub.org
  \item Join the Geargrinders Forum (search geargrinders) at http://groups.yahoo.com
\end{itemize}

\cleardoublepage

\pagenumbering{roman}

\tableofcontents

\cleardoublepage

\pagestyle{plain}

\pagenumbering{arabic}

\begin{center}
\line(1,0){250}
\end{center}
\input{procedures.tex}

\begin{center}
\line(1,0){250}
\end{center}
\input{rally-route.tex}

\begin{center}
\line(1,0){250}
\end{center}
\input{main-road-determinants.tex}

\begin{center}
\line(1,0){250}
\end{center}
\input{route-instructions.tex}

\begin{center}
\line(1,0){250}
\end{center}
\input{signs.tex}

\begin{center}
\line(1,0){250}
\end{center}
\input{glossary.tex}

%\appendix

\begin{center}
\line(1,0){250}
\end{center}
\input{appendix.tex}

\begin{center}
\line(1,0){250}
\end{center}
\input{points.tex}

\begin{center}
\line(1,0){250}
\end{center}
\input{TSD_formulas.tex}

\newpage

\begin{titlepage}
FINAL COVER
\end{titlepage}

\end{document}
